---
title: "Unsupervised Learning"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(rworldmap)
library(FactoMineR)
library(factoextra)
```

## Craigslist Vehicles

First, we are going to import the cleaned dataset.

```{r dataset import}
data <- read.csv("data/data_abe.csv")
data$X <- NULL # Remove the index from the csv
data <- na.omit(data) # Remove potential NA
dim(data)
colnames(data)
```

## 1. Geographical segmentation

We want to divide our American market into several regions. Nevertheless, we don't know how to properly define the regions, and how many regions we should have.

```{r visualise the dataset}
newmap <- getMap(resolution = "low")
xlim= c(min(data$long, na.rm=T), max(data$long, na.rm=T)) #long 
ylim= c(min(data$lat, na.rm=T), max(data$lat, na.rm=T)) #lat
plot(newmap, xlim = xlim, ylim = ylim, asp = 1)
points(data$long, data$lat, col = "red", cex = .6)
```

In order to solve this problem, we are going to use clustering on the latitude and longitude of our dataset. Let's find out how many clusters we should create.

```{r Clustering}
# We need to normalize our values
data$scaled_lat <- scale(data$lat)
data$scaled_long <- scale(data$long)
# First, let's find the optimal number of clusters
total_within_ss <- rep(0, times=10)
for(i in 1:10){
  km <- kmeans(data[, c("lat","long")], i)
  total_within_ss[i] <- km$tot.withinss
}
plot(total_within_ss, type="b",xlab="Number of clusters",ylab="Total within sum of squares", col="blue", lwd=1.5)
```

As we can see, applying the elbow rule, 3 seems to be the best number of clusters for our problem.
We are now going to apply the kmeans algorithm to our dataset and plot the generated clusters.

```{r Visualise the clusters}
km <- kmeans(data[, c("lat","long")], 3)
data$geographical_cluster <- km$cluster
newmap <- getMap(resolution = "low")
plot(newmap, xlim = xlim, ylim = ylim, asp = 1)
points(data[data$geographical_cluster == 1,]$long, data[data$geographical_cluster == 1,]$lat, col="blue", cex=.6)
points(data[data$geographical_cluster == 2,]$long, data[data$geographical_cluster == 2,]$lat, col="red", cex=.6)
points(data[data$geographical_cluster == 3,]$long, data[data$geographical_cluster == 3,]$lat, col="green", cex=.6)
legend("topleft", c("1","2", "3"), fill=c("blue","red", "green"))
```

Our recommandation for market geographical segmentation is to separate the country in three segments:
- Eastern
- Central
- Western

The boundaries are defined by the map printed earlier.

Finally, we will use the explained inertia metrics to evaluate our Kmeans algorithm.

```{r Evaluate our kmeans}
explaned_inertia <- rep(0,times=10)
for (k in 2:10){
  clus <- kmeans(data[, c("lat","long")],centers=k,nstart=5)  
  explaned_inertia[k] <- clus$betweenss/clus$totss
}

plot(1:10,explaned_inertia,type="b",xlab="Number of clusters",ylab="% explained inertia", col="blue", lwd=1.5)
```
